BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs

### 2013-11-04 tex/1-intro.tex
Extract the dataset blog contents and urls, included last suggestion from vangelis.
Move dataset to /dataset.

\section{Intro}
1-intro.tex
\begin{enumerate}
  \item Introduce the importance for blog preservation
  \item Explain the difficulties in harvesting blogs
  \item Explain why open source and Invenio
  \item Introduce the blog crawler
\end{enumerate}

>>>>

\section{Intro}

Aims and contributions of this work. Example from my last paper to see the format:
\surl{http://purl.pt/24107/1/iPres2013_PDF/CLEAR\%20a\%20credible\%20method\%20to\%20evaluate\%20website\%20archivability.pdf}

\begin{enumerate}
  \item Introduce the importance for blog preservation
  \item Explain the difficulties in harvesting blogs
  \item Explain why open source and Invenio
  \item Introduce the blog crawler
\end{enumerate}

Challenges consist of:
\begin{enumerate}
  \item Providing a high degree of automation
  \item Dealing with large volumes of data
\end{enumerate}

Semi-structured nature of Web pages

Labeled ordered rooted trees
XML Path Language(XPath)
